Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-23 RNARedPrint.tex

\section*{Methods}
The main computational problem addressed in this work is the design of sequences over the alphabet $\Sigma=\{\Ab,\Cb,\Gb,\Ub\}$, featuring a given $\GCb\%$, and compatible with a set of secondary structures, associated with prescribed free-energies.
Such criteria are here abstracted as constraints on the value of \Def{features}, functions of the sequence that are expressed as sums over real-valued contributions. Such contributions typically depend on the nucleotides assigned to a subset of sequence positions.

>>>>

\section*{Methods}
The main computational problem addressed in this work is the generation of sequences over the alphabet $\Sigma=\{\Ab,\Cb,\Gb,\Ub\}$, \revised{such that the sequences feature a given $\GCb\%$, and have prescribed energies for a set of target secondary structures.
Here, such criteria are modeled} as constraints on the value of \Def{features}, functions of the sequence that are expressed as sums over real-valued contributions. Such contributions typically depend on the nucleotides assigned to a subset of sequence positions.
